---
title: "Data Analyses"
---



#### Research Question: 
#### Is the fatality of a shooting incident associated with the victim's sex or race?

**1. Association between fatality and sex**

Method: Simple Logistic Regression

Hypotheses:

H<sub>0</sub>: There is no relationship between the independent variable (sex) and the response variable (fatality).

H<sub>a</sub>: There is a relationship between the independent variable (sex) and the response variable (fatality).

```{r}

summary(glm(data$fatal ~ data$sex, data = data, family = binomial))
```

**Interpretation:**

Since the p-value is less than 0.05, we can conclude that there is a significant relationship between the victim's sex and fatality of the shooting incident.

Compared to a female, the victim being a male increases the log odds of fatality by a factor of 0.3574 (or, would increase the odds of fatality by a factor of _e_<sup>0.3574</sup>=1.4296).



**2. Association between fatality and race**

Method: Simple Logistic Regression

Hypotheses:

H<sub>0</sub>: There is no relationship between the independent variable (race) and the response variable (fatality).

H<sub>a</sub>: There is a relationship between the independent variable (race) and the response variable (fatality).

```{r}

summary(glm(data$fatal ~ data$race, data = data, family = binomial))

```


**Interpretation:**

Since the p-values are greater than 0.05, we can conclude that there is no significant relationship between the victim's race and fatality of the shooting incident.



I will discuss the results and conclusions in the next page.

