---
title: "Data"
---



**Description of data**

The data file is accessed from https://www.opendataphilly.org/dataset/shooting-victims


It records shooting incidents in Philadelphia from 2015 until March 2018 (when I downloaded the file).

My initial data cleaning process includes:

1. Deleted the file column that records the file numbers that are irrelevant for the analyses

2. Removed data entries with N/A values

3. Reconciled "sex" and "race" columns, so that one level is only represented by one value (e.g. "male"" is only represented by "M", not "m"; "Black" is only represented by "B", not "b", etc.)

**1. Overall Description**
```{r}
data = read.csv("shooting_data.csv")

# Number of data entries
nrow(data)

# Column names
colnames(data)

```

**2. Sex**

First, take a look at the "sex" data

```{r}
# Data type
class(data$sex)

# "Sex"is a categorical data

# What are the values?
levels(data$sex)

# Make a table with counts
table(data$sex)

# Draw a plot
plot(data$sex, main = "Gender")

```

**3. Race**

Next, take a look at the "race" data

```{r}
# Data type
class(data$race)

# "Race" is also a categorical data

# What are the values?
levels(data$race)

# Make a table with counts
table(data$race)

# Draw a plot
plot(data$race, main = "Race")

```

**4. Fatality**

The column "fatal" records the number of fatalities in each of the shooting incident.

```{r}
# Data type
class(data$fatal)

# Since it is an interger data, use a table to show values 
table(data$fatal)
```

The values are either "0" or "1", which means that when fatal shooting incidents happened, the number of fatalies was always 1 (fortunately). 

Therefore, we can treat it as a categorical variable, with "1" denoting a certain shooting incident involves fatality and "0" denoting the opposite.

```{r}
# Treat "fatal" as categorical variable
data$fatal = as.factor(data$fatal)
levels(data$fatal)

# Draw a plot
plot(data$fatal, main = "Fatality")

```



After taking a close look at these key variables, I will use the next page to show my data analyses for the research questions.

